### 2016-10-14 mcmc.tex
constraints

@@

%% HOGG DELETED / COMMENTED OUT THE BELOW
%% - make sure everything below is discussed somewhere above and then delete it below.

%% ...breaking Markov-ness.
%% % ***** BJB
%% % "Diminishing adaptations" is an idea that is quite easy
%% % to explain. There are other ways to break Markov-ness but
%% % this probably covers enough of them for an intro document
%% % ***** Hogg
%% % I was going to say you should NEVER break Markov-ness
%% % unless you REALLY understand what you are doing.

%% ...Posteriors:  You can do anything you like (within
%% reason) to the output samples and be sampling the posterior in that
%% transformed quantity.

%% ...How to deal with constraints that pin you to a subspace of the parameter space?  Method-dependent.

>>>>

For yet another example, there might be constraints such that all
acceptable models lie on a non-trivial, non-linear subspace of your
parameter space.
Here almost no arbitrary steps in parameter space could lead to an
acceptance, since if you move arbitrarily, you are very unlikely to
hit the subspace!
Your best move here is to re-parameterize so there are only models on
that subspace.
We're not claiming that that re-parameterization is always easy to
find; the mathematics of Lagrange multipliers can be useful here.

@@
